### 2024-09-22 cognitive-bias.qmd
20240922 - additional info

As described [above](#sec-cognitiveBiasOverview), cognitive biases are systematic errors in thinking.
They lead us to be less accurate in our judgments and predictions.
Inaccuracy may not always be bad; several cognitive biases may serve to help people feel better about themselves [@Miller2013c], including [confirmation bias](#sec-cognitiveBiasesConfirmation), [overconfidence bias](#sec-cognitiveBiasesOverconfidence), [optimism bias](#sec-cognitiveBiasesOptimism), and [self-serving bias](#sec-cognitiveBiasesSelfServing).
In fantasy football, however, cognitive biases and inaccurate judgments can lead to worse performance.
Cognitive biases are often due to the use of [heuristics](#sec-heuristics).

@@

*Omission bias* is the tendency to prefer inaction over action, or to prefer the default option over changes from the default option [@Kahneman2011].
For instance, consider a manager who is on the fence to drop an underperforming player and to pick up someone else to start.
If the manager does not drop the player and the player scores few points, the manager is likely to be less critical and regretful of their decision than if they had picked up another player who then scored the same (low) number of points.
Thus, a person's decisions may be influenced by the anticipation of regret so as to keep the status quo, avoid losses, and minimize the expectation of regret—such as choosing the same order each time at a restaurant to avoid regret [@Kahneman2011].
However, people may anticipate more regret than they actually experience, because people tend to underestimate the protective impact of the psychological defenses they will deploy against regret [@Kahneman2011].
In general, @Kahneman2011 recommends not to put too much weight on potential future regret when making decisions: "even if you have some [regret], it will hurt less than you now think." (p. 352).

@@

Pay attention to players' usage and opportunities, not just how many points a player scored and whether they had more fumbles or interceptions than other players.
The more times a player touches the ball, the more points they are likely to score.

@@

A *sunk cost* is a cost (e.g., in money, time, or effort) that has already been incurred and cannot be recovered.
For instance, if a person orders an expensive meal at a restaurant, the order is a sunk cost.
The *sunk cost fallacy* is the tendency to continue an endeavor when there is a sunk cost.
For instance, when ordering the expensive meal at the restaurant, a person may over-eat so that they feel that they eat their money's worth of food.
The sunk cost fallacy is an example of the commitment bias, an escalation of commitment by which a person continues to commit additional time, effort, or resources to a failing project.
It is important to be willing to identify and terminate failing projects to cut one's losses.

>>>>

As described [above](#sec-cognitiveBiasOverview), cognitive biases are systematic errors in thinking.
They lead us to be less accurate in our judgments and predictions.
Inaccuracy may not always be bad; several cognitive biases may serve to help people feel better about themselves [@Miller2013c], including [confirmation bias](#sec-cognitiveBiasesConfirmation), [overconfidence bias](#sec-cognitiveBiasesOverconfidence), [optimism bias](#sec-cognitiveBiasesOptimism), and [self-serving bias](#sec-cognitiveBiasesSelfServing); or to prevent feelings of regret (e.g., [omission bias](#sec-cognitiveBiasesOmission))—or to prevent having to admit failure (e.g., [commitment bias](#sec-fallaciesSunkCost)).
In fantasy football, however, cognitive biases and inaccurate judgments can lead to worse performance.
Cognitive biases are often due to the use of [heuristics](#sec-heuristics).

@@

*Omission bias* is the tendency to prefer inaction over action, or to prefer the default option over changes from the default option [@Kahneman2011].
For instance, consider a manager who is on the fence to drop an underperforming player and to pick up someone else to start.
If the manager does not drop the player and the player scores few points, the manager is likely to be less critical and regretful of their decision than if they had picked up another player who then scored the same (low) number of points.
Thus, a person's decisions may be influenced by the anticipation or fear of regret so as to keep the status quo, avoid losses, and minimize the expectation of regret—such as choosing the same order each time at a restaurant to avoid regret [@Kahneman2011].
However, people may anticipate more regret than they actually experience, because people tend to underestimate the protective impact of the psychological defenses they will deploy against regret [@Kahneman2011].
In general, @Kahneman2011 recommends not to put too much weight on potential future regret when making decisions: "even if you have some [regret], it will hurt less than you now think." (p. 352).

@@

Pay attention to players' usage and opportunities, not just how many points a player scored and whether they had more fumbles or interceptions than other players.
The more times a player touches the ball, the more points they are likely to score.
And do not let the anticipation of regret prevent you from making important decisions.

@@

A *sunk cost* is a cost (e.g., in money, time, or effort) that has already been incurred and cannot be recovered.
For instance, if a person orders an expensive meal at a restaurant, the order is a sunk cost.
The *sunk cost fallacy* is the tendency to continue an endeavor when there is a sunk cost.
For instance, when ordering the expensive meal at the restaurant, a person may over-eat so that they feel that they eat their money's worth of food.
The sunk cost fallacy is an example of the *commitment bias*, an *escalation of commitment* by which a person continues to commit additional time, effort, or resources to a failing project.
People tend to refuse to cut their losses when doing so would admit failure [@Kahneman2011].
It is important to be willing to identify and terminate failing projects to cut one's losses.
